---
format: revealjs
---

## Today's Agenda {background-image="Images/00-Leviathan_Cover_55.png" .center}

```{r}
library(tidyverse)
library(readxl)
library(kableExtra)

# Data for today
library(carData)
```

<br>

**II. How and why do governments use violence against the people inside their borders?**

<br>

Working on the Country Briefings

<br>

::: r-stack
Justin Leinaweaver (Fall 2025)
:::

::: notes
Prep for Class

1. Review submissions on Canvas

<br>

**SLIDE**: Paper prompt

:::




## Paper 2 {background-image="Images/00-Leviathan_Cover_55.png" .center}

Political Violence Country Briefings

Select **two countries** (no overlapping cases in class) and analyze their recent experience of political violence using **ALL FIVE** of the data sources we explored in class

For **EACH** country you must produce a **TWO PAGE** country briefing report that summarizes and visualizes the findings of your analyses

- 2 countries x 2 pages = 4 pages total

- You should aim to analyze at least the last five years of available data for each country.

::: notes

**Questions on the assignment?**

:::



## For Today {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### **Prepare at least three conclusions about EACH country's experience of political violence (with visualizations)**

1. Tables 

2. Bar Plots

3. Line Plots

4. Scatter Plots

::: notes

**Everybody ready to go with this?**

<br>

**SLIDE**: Before we review your work, let's refresh our criteria of professional visualizations

:::



## Visualizations MUST include {background-image="Images/background-data_blue_v4.png" .center .smaller}

:::: {.columns}
::: {.column width="50%"}
```{r, fig.align='center', fig.asp=1.1, fig.width=6, fig.cap="Figure 1. A count of countries by regional grouping from the United Nations (2009-2011) that shows the great majority of countries in the UN are located in Africa and Asia."}
# The labs() function
library(carData)

ggplot(data = UN, aes(y = region)) +
  geom_bar() +
  labs(x = "x Axis Label", y = "y Axis Label", 
       title = "A title like a thesis statement for the visualization")

# caption = "Source: Where did the data come from?"
```

:::

::: {.column width="50%"}

::: {.r-fit-text}
1. Informative titles,

2. Clear axis labels, and

3. A figure caption with

    - Data sources
    
    - Description, and
    
    - Conclusions
:::
:::
::::

::: notes

**Questions on these?**

<br>

**SLIDE**: Let's review the submissions!

:::



## Peer-Review Time! {background-image="Images/background-data_blue_v4.png" .center}

<br>

1. Is each conclusion MORE than a simple description?

2. Is the proposed data visualization sufficient for supporting this conclusion?

::: notes


:::




## For Next Class {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Revise and Resubmit with POLISHED visualizations**
:::

::: notes



<br>

**Questions on the assignment?**

:::