---
format: revealjs
---

## Today's Agenda {background-image="Images/00-Leviathan_Cover_55.png" .center}

```{r}
library(tidyverse)
library(readxl)
library(kableExtra)

# Data for today
library(carData)
```

<br>

**II. How and why do governments use violence against the people inside their borders?**

- Working on the Country Briefings

<br>

::: r-stack
Justin Leinaweaver (Fall 2025)
:::

::: notes
Prep for Class

1. Review submissions on Canvas

<br>

**SLIDE**: Paper prompt

:::




## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Paper 2: Political Violence Country Briefings**
:::

<br>

Select TWO countries and analyze their government's use of political violence

- Must cover the most recently available **five years** of data

- Must reference **ALL FIVE** of the data sources

- Argument must include **three** distinct premises

- Two pages (**max**) per country

::: notes

**Questions on the assignment?**

:::



## For Today {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

Submit an outline of each country briefing report

- One sentence thesis statement

- Each premise gets a one sentence explanation and a draft version of the data summary you intend to use to support it (e.g. a table or a visualization)

::: notes

For today I asked everyone to submit an outline of their briefings to Canvas

- The idea is to help you break this exercise down into simpler pieces, AND

- To help you understand that the conclusions you draw from the data are meant to support bigger ideas (e.g. premises in your argument)

<br>

**How did this go for you?**

<br>

**SLIDE**: Peer review time

:::


## Peer-Review Time! {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

::: {.incremental}

1. Critical Analysis: Is each premise MORE than a simple description of the data?

2. Credibility: Is the proposed data visualization sufficient for supporting this premise?

3. Meso Structure: Do the proposed premises build logically from one to the next?

:::

::: notes

Your job today is to help your classmates and yourself get ready to execute this project to the best of your ability.

- I want you to take time to pair off with EVERYONE else in the class

- Your job is to review their outline and give them ideas to make it stronger or more compelling

- This way everyone gets tons of feedback AND sees a bunch of other projects with a similar aim under development

<br>

I would like to encourage each of you to focus your feedback on three things:

- **REVEAL x 3**

<br>

**Any questions on this task?**

- Go!

<br>

**Which outlines stood out to you as most compelling? Why?**

<br>

**Did everybody come away with some good ideas for attacking these country briefings?**

<br>

**SLIDE**: Before we push to the next step, let's refresh our criteria of professional visualizations

:::






## Visualizations MUST include {background-image="Images/background-data_blue_v4.png" .center .smaller}

:::: {.columns}
::: {.column width="50%"}
```{r, fig.align='center', fig.asp=1.1, fig.width=6, fig.cap="Figure 1. A count of countries by regional grouping from the United Nations (2009-2011) that shows the great majority of countries in the UN are located in Africa and Asia."}
# The labs() function
library(carData)

ggplot(data = UN, aes(y = region)) +
  geom_bar() +
  labs(x = "x Axis Label", y = "y Axis Label", 
       title = "A title like a thesis statement for the visualization")

# caption = "Source: Where did the data come from?"
```

:::

::: {.column width="50%"}

::: {.r-fit-text}
1. Informative titles,

2. Clear axis labels, and

3. A figure caption with

    - Data sources
    
    - Description, and
    
    - Conclusions
:::
:::
::::

::: notes

These are the same criteria I held you to in Data Analysis.

- **Any questions on these?**

<br>

**SLIDE**: For next class!

:::



## For Next Class {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

Revise and resubmit the outlines from today based on the feedback and your continued reflections on the assignment.

- Each outline must begin with a one sentence thesis statement.

- Each premise (of the three) gets a complete sentence explaining it and a POLISHED version of the data summary you intend to use to support it (e.g. informative titles, clear axis labels, no chart junk, etc.) 

::: notes

Revise and resubmit the outlines from last class based on the feedback from class and your continued reflections on the assignment.

- Each outline must begin with a one sentence thesis statement.

- Each premise (of the three) gets a complete sentence explaining it and a POLISHED version of the data summary you intend to use to support it (e.g. informative titles, clear axis labels, no chart junk, etc.) 


<br>

**Questions on the assignment?**

:::