---
format: revealjs
---

## Today's Agenda {background-image="Images/00-Leviathan_Cover_55.png" .center}

```{r}
library(tidyverse)
library(readxl)
library(kableExtra)

# Data for today
library(carData)
```

<br>

**II. How and why do governments use violence against the people inside their borders?**

<br>

- Polishing the Country Briefings

<br>

::: r-stack
Justin Leinaweaver (Fall 2025)
:::

::: notes
Prep for Class

1. Review submissions on Canvas

<br>

**SLIDE**: Paper prompt

:::




## Paper 2 {background-image="Images/00-Leviathan_Cover_55.png" .center}

Political Violence Country Briefings

Select **two countries** (no overlapping cases in class) and analyze their recent experience of political violence using **ALL FIVE** of the data sources we explored in class

For **EACH** country you must produce a **TWO PAGE** country briefing report that summarizes and visualizes the findings of your analyses

- 2 countries x 2 pages = 4 pages total

- You should aim to analyze at least the last five years of available data for each country.

::: notes

**Questions on the assignment?**

<br>

For today I asked everyone to revise and resubmit their outlines with polished visualizations

- **SLIDE**: what is a polished visualization?

:::


## Visualizations MUST include {background-image="Images/background-data_blue_v4.png" .center .smaller}

:::: {.columns}
::: {.column width="50%"}
```{r, fig.align='center', fig.asp=1.1, fig.width=6, fig.cap="Figure 1. A count of countries by regional grouping from the United Nations (2009-2011) that shows the great majority of countries in the UN are located in Africa and Asia."}
# The labs() function
library(carData)

ggplot(data = UN, aes(y = region)) +
  geom_bar() +
  labs(x = "x Axis Label", y = "y Axis Label", 
       title = "A title like a thesis statement for the visualization")

# caption = "Source: Where did the data come from?"
```

:::

::: {.column width="50%"}

::: {.r-fit-text}
1. Informative titles,

2. Clear axis labels, and

3. A figure caption with

    - Data sources
    
    - Description, and
    
    - Conclusions
:::
:::
::::

::: notes

**Questions on these?**

<br>

**SLIDE**: Let's review the submissions!

:::



## Peer-Review Time! {background-image="Images/background-data_blue_v4.png" .center}

<br>

1. Is the argument well supported by evidence?

2. Is the evidence visualized "professionally"?
    - Informative title
    - Figure label and caption
    - Source information
    - Clear axes and labels
    - No chart junk or wasted space

3. Are you convinced by the argument?

::: notes

*Split class into pairs*

Pairs, present your argument to your partner.

- Partners you have three jobs

<br>

### Questions?

- Let's go!

<br>

### Any really great examples to share?

:::




## For Next Class {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
1. Country Briefings due Oct 17th

2. Next Week: Let's find some acts of terrorism!
:::

::: notes

Canvas Assignment: Terrorism Case Studies 

Submit to Canvas a recent example of an individual committing what you believe should be classified as an act of terrorism.

1. Submit an APA citation to evidence/background of your selected act
2. Describe the specifics of the case (actor, action, date, impact),
3. Make an argument as to why you believe this is an act of terrorism (3+ sentences)

<br>

**Questions on the assignment?**

:::














