---
format: revealjs
---

## Today's Agenda {background-image="Images/00-Leviathan_Cover_55.png" .center}

```{r}
library(tidyverse)
library(readxl)
library(kableExtra)
```

<br>

**II. How and why do governments use violence against the people inside their borders?**

<br>

- Finishing the Country Briefings

<br>

::: r-stack
Justin Leinaweaver (Fall 2025)
:::

::: notes
Prep for Class

1. Review submissions on Canvas

2. Move quickly onto the second exercise (adding nuance to the plots!)

<br>

**SLIDE**: Paper prompt

:::




## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Paper 2: Political Violence Country Briefings**
:::

<br>

Select TWO countries and analyze their government's use of political violence

- Must cover the most recently available **five years** of data

- Must reference **ALL FIVE** of the data sources

- Argument must include **three** distinct premises

- Two pages (**max**) per country

::: notes

**Questions on the assignment?**

<br>

For today I asked everyone to revise and resubmit their outlines with polished visualizations

- **SLIDE**: Reminder, what is a polished visualization?

:::


## Visualizations MUST include {background-image="Images/background-data_blue_v4.png" .center .smaller}

:::: {.columns}
::: {.column width="50%"}
```{r, fig.align='center', fig.asp=1.1, fig.width=6, fig.cap="Figure 1. A count of countries by regional grouping from the United Nations (2009-2011) that shows the great majority of countries in the UN are located in Africa and Asia."}
# The labs() function
library(carData)

ggplot(data = UN, aes(y = region)) +
  geom_bar() +
  labs(x = "x Axis Label", y = "y Axis Label", 
       title = "A title like a thesis statement for the visualization")

# caption = "Source: Where did the data come from?"
```

:::

::: {.column width="50%"}

::: {.r-fit-text}
1. Informative titles,

2. Clear axis labels, and

3. A figure caption with

    - Data sources
    
    - Description, and
    
    - Conclusions
:::
:::
::::

::: notes

**Questions on these?**

<br>

**SLIDE**: Let's review the submissions!

:::




## Peer-Review Time! {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

1. Is the argument clear and well supported by the evidence?

2. Is the evidence visualized "professionally"?
    - Informative title
    - Figure label and caption
    - Source information
    - Clear axes and labels
    - No chart junk or wasted space

3. Are you convinced by the argument?

::: notes

Just like last class your job is to see and give feedback on ALL of the outlines!

- Please focus your feedback on these big picture elements

<br>

**Questions?**

- Let's go!

<br>

Let's share some excellent examples!

- Call out some classmates who are producing high quality work so we can celebrate it!

<br>

**SLIDE**: Time to add more nuance!

:::



## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**How do we make these visualizations even better?**
:::

```{r, fig.retina=3}
d <- read_excel("../../Data/PTS/2024-08/PTS-2024.xlsx", na = "NA")

d |>
  filter(Year >= 1979, Year < 1984, Country == "Uganda") |> 
  ggplot(aes(x = Year, y = PTS_S)) +
  geom_line() +
  theme_bw() +
  ylim(0,5.2) +
  labs(x = "", y = "Political Terror Scale Score",
       title = "Political violence in Uganda is a growing threat to the mass public")

```

::: notes

Ok, so we've got a basic line plot with an informative title and hopefully some good info in the figure caption

- HOWEVER, the reader isn't an expert in the PTS and doesn't really understand what these numbers mean

<br>

**SO, what can we do to add more nuance and analyses to our visualizations?**

- **Especially needed if your line or bar plot shows little to no variation AND the reader is not an expert in these measures**

<br>

*Let the class BRAINSTORM and discuss*

<br>

**SLIDE**: Option 1, label the hinge points

:::



## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Option 1: Label the Hinge Points**
:::

```{r, fig.retina=3}
d |>
  filter(Year >= 1979, Year < 1984, Country == "Uganda") |> 
  ggplot(aes(x = Year, y = PTS_S)) +
  geom_line() +
  theme_bw() +
  ylim(0,5.2) +
  labs(x = "", y = "Political Terror Scale Score",
       title = "Political violence in Uganda is growing threat to the mass public") +
  annotate("text", x = 1979, y = 1.8, srt = 90, label = "War with Tanzania", color = "red", size = 4, adj = 1) +
  annotate("text", x = 1980, y = 3.8, srt = 90, label = "Military coup d'etat", color = "red", size = 4, adj = 1) +
  annotate("text", x = 1981, y = 3.8, srt = 90, label = "Obote government established", color = "red", size = 4, adj = 1)

```

::: notes

Add labels to hinge points: Explain on the plot why changes occur in a given year (e.g. 2023 coup)

<br>

**SLIDE**: Option 2 add comparison countries

:::



## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Option 2: Add Comparison Countries**
:::

```{r, fig.retina=3}

d1 <- d |>
  filter(Year >= 1979, Year < 1984, Country == "Uganda")

d2 <- d |>
  filter(Year >= 1979, Year < 1984, Country == "Tanzania, United Republic of")

ggplot() +
  geom_line(data = d1, aes(x = Year, y = PTS_S), color = "orange3") +
  geom_line(data = d2, aes(x = Year, y = PTS_S), color = "darkblue", linetype = "dashed") +
  theme_bw() +
  ylim(0,5.2) +
  labs(x = "", y = "Political Terror Scale Score",
       title = "Uganda and Tanzania have had very different post-war experiences") +
  annotate("text", x = 1983, y = 4.7, adj = 1, label = "Uganda", color = "orange3") +
  annotate("text", x = 1983, y = 2.25, adj = 1, label = "Tanzania", color = "darkblue")

```

::: notes

In 1978-1979 Tanzania and Uganda fought a war

- The war devastated Tanzania's economy, but it completely upended Uganda

<br>

**SLIDE**: Option 3 add descriptive stats

:::



## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Option 3: Add Descriptive Statistics**
:::

```{r, fig.retina=3}
# Subsaharan Africa
ssa_avg <- d |>
  filter(Year >= 1979, Year < 1984, Region == "ssa") |>
  summarize(
    Avg = mean(PTS_S, na.rm = TRUE)
  )

d |>
  filter(Year >= 1979, Year < 1984, Country == "Uganda") |> 
  ggplot(aes(x = Year, y = PTS_S)) +
  geom_line() +
  theme_bw() +
  ylim(0,5.2) +
  labs(x = "", y = "Political Terror Scale Score",
       title = "Political violence in Uganda is growing threat to the mass public") +
  geom_hline(yintercept = ssa_avg[[1]], linetype = "dashed", color = "darkred") +
  annotate("text", x = 1982.5, y = 1.85, label = "Average in Sub-Saharan Africa", color = "darkred")

```

::: notes

Add global averages or averages for other groups (OECD, G77, etc)

<br>

**Questions on these techniques?**

<br>

**SLIDE**: Assignment

:::




## For Next Class {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
1. Country Briefings due Oct 17th

2. Next Week: Find me acts of terrorism!
:::

::: notes

Briefings are due this week and after the break we dive headfirst into terrorism!

- That sounded wrong...

<br>

**Questions on the assignment?**

- Have a good fall break!

<br>

Canvas Assignment: Terrorism Case Studies 

Submit to Canvas a recent example of an individual committing what you believe should be classified as an act of terrorism.

1. Submit an APA citation to evidence/background of your selected act
2. Describe the specifics of the case (actor, action, date, impact),
3. Make an argument as to why you believe this is an act of terrorism (3+ sentences)

:::














