---
format: revealjs
---

## Today's Agenda {background-image="Images/00-Leviathan_Cover_55.png" .center}

```{r}
library(tidyverse)
library(readxl)
library(kableExtra)

# Data for today
library(carData)
```

<br>

**II. How and why do governments use violence against the people inside their borders?**

<br>

- Finishing the Country Briefings

<br>

::: r-stack
Justin Leinaweaver (Fall 2025)
:::

::: notes
Prep for Class

1. Review submissions on Canvas

<br>

**SLIDE**: Paper prompt

:::




## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Paper 2: Political Violence Country Briefings**
:::

<br>

Select TWO countries and analyze their government's use of political violence

- Must cover the most recently available **five years** of data

- Must reference **ALL FIVE** of the data sources

- Argument must include **three** distinct premises

- Two pages (**max**) per country

::: notes

**Questions on the assignment?**

<br>

For today I asked everyone to revise and resubmit their outlines with polished visualizations

- **SLIDE**: Reminder, what is a polished visualization?

:::


## Visualizations MUST include {background-image="Images/background-data_blue_v4.png" .center .smaller}

:::: {.columns}
::: {.column width="50%"}
```{r, fig.align='center', fig.asp=1.1, fig.width=6, fig.cap="Figure 1. A count of countries by regional grouping from the United Nations (2009-2011) that shows the great majority of countries in the UN are located in Africa and Asia."}
# The labs() function
library(carData)

ggplot(data = UN, aes(y = region)) +
  geom_bar() +
  labs(x = "x Axis Label", y = "y Axis Label", 
       title = "A title like a thesis statement for the visualization")

# caption = "Source: Where did the data come from?"
```

:::

::: {.column width="50%"}

::: {.r-fit-text}
1. Informative titles,

2. Clear axis labels, and

3. A figure caption with

    - Data sources
    
    - Description, and
    
    - Conclusions
:::
:::
::::

::: notes

**Questions on these?**

<br>

**SLIDE**: Let's review the submissions!

:::




## Peer-Review Time! {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

1. Is the argument clear and well supported by the evidence?

2. Is the evidence visualized "professionally"?
    - Informative title
    - Figure label and caption
    - Source information
    - Clear axes and labels
    - No chart junk or wasted space

3. Are you convinced by the argument?

::: notes

Just like last class your job is to see and give feedback on ALL of the outlines!

- Please focus your feedback on these big picture elements

<br>

**Questions?**

- Let's go!

<br>

Let's share some excellent examples!

- Call out some classmates who are producing high quality work so we can celebrate it!

<br>

**SLIDE**: Assignment

:::




## For Next Class {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
1. Country Briefings due Oct 17th

2. Next Week: Find me acts of terrorism!
:::

::: notes

Briefings are due this week and after the break we dive headfirst into terrorism!

- That sounded wrong...

<br>

**Questions on the assignment?**

- Have a good fall break!

<br>

Canvas Assignment: Terrorism Case Studies 

Submit to Canvas a recent example of an individual committing what you believe should be classified as an act of terrorism.

1. Submit an APA citation to evidence/background of your selected act
2. Describe the specifics of the case (actor, action, date, impact),
3. Make an argument as to why you believe this is an act of terrorism (3+ sentences)

:::














