---
format: revealjs
---

## Today's Agenda {background-image="Images/00-Leviathan_Cover_55.png" .center}

```{r}
library(tidyverse)
library(readxl)
library(kableExtra)
```

<br>

**III. How and why do non-state actors use political violence?**

<br>

- Brainstorming a political violence research project

<br>

::: r-stack
Justin Leinaweaver (Fall 2025)
:::

::: notes
Prep for Class

1. Review submissions on Canvas

2. Markers x 4

<br>

This semester we have taken a scientific approach to studying political violence

- We've worked to clarify our key concepts,

- We've explored high quality academic research, 

- We've examined the data projects that exist to measure political violence, and

- We've continuously tried to connect our work to the real world.

<br>

This week we've been exploring some of the cutting-edge research into terrorism

- Specifically the debate about the existence of a new "wave" of terror reflecting a rise in far-right terrorism (FRT)

- We've examined a research article and explored a data source that could help us measure and analyze the trends across time (in the US at least)

<br>

Today I want us to pivot from critically analyzing research to setting ourselves up to do new and useful research!

<br>

**Ok, remind me, why does a research project need to begin with a research question?**

- (**SLIDE**)

:::



## Why do we need a research question? {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

A research question **focuses** your work, **drives** your progress and let's you know when you're **done**

::: notes

We hit these elements pretty hard in the methods track in our major

- e.g. Political Inquiry, Data Analysis, Research Design and Senior Seminar

<br>

In short, science is driven forward by questions

- Without a question you really can't figure out what is and isn't relevant to your project

-  And that last point is key, if you're not answering a question how on Earth do you ever know if you're done?

<br>

**Refresh my memory, what makes a question a "research" question?**

- (**SLIDE**: Per Huntington-Klein there are two requirements)

:::



## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Research Questions (Huntington-Klein 2022)**

1. Can be answered

:::

::: notes

FIRST, a research question can be answered

- That means it is possible for there to be some set of evidence in the world that could be used to answer your question

<br>

**What's an example of a question we cannot answer with evidence?**

- (The book chapter gives us an example: what is the best James Bond movie?)

    - Couldn't you just run a survey? Nope, that's a measure of "popularity", not "quality"  

<br>

**SLIDE**: Criteria 2

:::



## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Research Questions (Huntington-Klein 2022)**

1. Can be answered

2. Improves our understanding of the world

:::

::: notes

SECOND, research questions produce answers that improve your understanding of how the world works.

- The question and answer should inform theory in some way.

<br>

Theory just means that there’s a *why* underpinning your view of the world

- Theory explains why we think the relationships we see in the world are happening 

- Theory is the simplified story we tell to explain why thing's happen

<br>

You almost certainly have a million intuitions about how and why the world works like it does.

- Our aim is to design research projects that force us to clarify these assumptions in order to test them with empirical data.

- A good research question helps us begin that process

<br>

**SLIDE**: The second criteria reinforced...

:::



## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Research Questions (Huntington-Klein 2022)**

1. Can be answered

2. Improves our understanding of the world

:::

<br>

"A good test for whether a research question informs theory is to imagine that you find an unexpected result, and then wonder whether it would make you change your understanding of the world."

::: notes

I especially like this advice from Huntington-Klein on the second criteria.

- A good RQ should have stakes!

- If getting an answer you didn't expect forces you to rethink how the world works, that's a good question!

<br>

**Any questions on these two basic requirements of a research question?**

<br>

**SLIDE**: Huntington-Klein also offers us criteria for analyzing a RQ

:::



## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Research Questions (Huntington-Klein 2022)**
:::

<br>

**How Do You Know if You’ve Got a Good One?**

- Consider Potential Results

- Consider Feasibility

- Consider Scale

- Consider Design

- Keep It Simple!


::: notes

Per Huntington-Klein, we should focus our research efforts on questions we are likely able to answer with the resources available to us.

<br>

That means we should: 

- **Consider Potential Results**: "If you can’t say something interesting about your potential results, that probably means your research question and your theory aren’t as closely linked as you think!"

- **Consider Feasibility**: "A research question should be a question that can be answered using the right data, if the right data is available. But is the right data available?"

- **Consider Scale**: "What kind of resources and time can you dedicate to answering the research question? ... Given the confines of, say, a term paper, you could take some wild swings at that question, but you’re likely to do a much more thorough job answering questions with a lot less complexity."

- **Consider Design**: "So, an important part of evaluating whether you have a workable research question is figuring out if there’s a reasonable research design you can use to answer it. Figuring out whether you do have a reasonable research design is the topic of the rest of this book."

- **Keep It Simple!**: "Answering any research question can be difficult. Don’t make it even harder on yourself by biting off more than you can chew!"

<br>

So, a research question:

1. Can be answered,

2. Improves our understanding of the world, and 

3. Is feasible given our reseources

<br>

**Questions on any of this?**

<br>

**SLIDE**: To your work!

:::




## For Today {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### Research Questions to Explore the New Wave of Terrorism

::: notes

For today I asked each of you to submit and explain a research question we could use to push forward our knowledge of terrorism in the world today.

- **Everybody ready to go with this?**

<br>

*Split class into four groups, work with new people!*

- *I'd prefer smaller groups BUT there's only so much board space*

- Go sit with your new group!

<br>

**SLIDE**: Groups choose/refine a research question

:::



## Developing a Research Proposal {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### 1. Select a research question for your group

- Write the question on the board

- Draw a simple DAG below the question

```{r, fig.retina = 3, fig.align = 'center', fig.width = 6, fig.height=.85, out.width='85%'}
## Manual DAG
d1 <- tibble(
  x = c(-3, 3),
  y = c(1, 1),
  labels = c("Predictor", "Outcome")
)

ggplot(data = d1, aes(x = x, y = y)) +
  geom_point(size = 8) +
  theme_void() +
  coord_cartesian(xlim = c(-4, 4)) +
  geom_label(aes(label = labels), size = 7) +
  annotate("segment", x = -1.9, xend = 1.9, y = 1, yend = 1, arrow = arrow())
```

::: notes

Groups, pick the RQ you want to work on in class today

- Can be one of the ones submitted to Canvas or something new

<br>

Once you have your RQ:

1. Write it on the board, and

2. Summarize the question with a directed acyclic graph (DAG)

<br>

**Questions?**

- Go!

<br>

*PRESENT and DISCUSS each*

- Groups, take a moment to address the feedback you get from this

<br>

**SLIDE**: Theory

:::



## Developing a Research Proposal {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### 2. Propose a theory

- List the reasons your predictor causes your outcome

::: notes

Groups, your next job is to propose a theory that answers this question

- In other words, you need to explain the arrow in the DAG

<br>

Think of this like diagramming an argument

- You are arguing that these two concepts are linked by a causal mechanism (e.g. changes in the predictor lead to changes in the outcome)

- Give us the reasons on the board WHY you think this is true

<br>

**Questions?**

- Go!

<br>

*PRESENT and DISCUSS each*

- Groups, take a moment to address the feedback you get from this

<br>

**SLIDE**: Data needs

:::



## Developing a Research Proposal {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### 3. Describe your data needs

- What is the ideal type of data you would need?

- Do a web search and see if it exists

::: notes

Groups, you now have a question and a theory that suggests an answer to it

- The next step is to identify the kinds of specific measures you would need to answer this question and test your theory

<br>

1. Make sure you understand what kind of measures you would need to answer your question, then

2. Do a simple web search and look to see if this data exists!

<br>

**Questions?**

- Go!

<br>

*PRESENT and DISCUSS each*

<br>

**SLIDE**: Wrap it up

:::



## For Today {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### Research Questions to Explore the New Wave of Terrorism

::: notes

**Ok, where do we end up with this?**

- **Groups, do you feel like you have the makings of a real research project here? One that is doable AND would improve our understanding of the world?**

<br>

**Any lessons for the next time you do an exercise like this?**

- **Anything you've learned from this you would apply next time?**

<br>

**SLIDE**: Next class

:::



## For Next Class {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### The Future of Terrorism

Bring to class **TWO** examples of the internet changing terrorism as a political strategy. 

1. A terror group changing its operational behavior, and

2. States changing how they combat terrorism

::: notes

Details on Canvas

- **Questions on the assignment?**

<br>

Canvas Assignment: The Internet and Terrorism

Bring to class TWO examples of the internet changing terrorism as a political strategy. 

For each case, submit:

- An APA citation,
- An explanation for what happened, and
- An explanation of why you believe this case illustrates something important in the evolution of terrorism

1. For the first case find us an example of the internet changing the operational behavior of terror groups. For example, has the internet changed how terror groups recruit, choose their targets or decide the method for their attacks?

2. For the second case find us an example of the internet changing how states combat terrorism.

:::





