---
format: revealjs
---

## Today's Agenda {background-image="Images/00-Leviathan_Cover_55.png" .center}

```{r}
library(tidyverse)
library(readxl)
library(kableExtra)
```

<br>

**III. How and why do non-state actors use political violence?**

<br>

- Brainstorming a political violence research project

<br>

::: r-stack
Justin Leinaweaver (Fall 2025)
:::

::: notes
Prep for Class

1. Review submissions on Canvas

2. Markers x 4

<br>

**SLIDE**: IDEA evals

:::




## Course Evaluations (IDEA) {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

::: {.r-fit-text}
[https://drury.campuslabs.com/eval-home/](https://drury.campuslabs.com/eval-home/)
:::

::: notes

The link for the IDEA evaluations is here.

- I'll give you ten minutes to complete them

- Super important feedback and I appreciate you taking the time to do it

<br>

IFF everyone in class submits their evals for this class I will give everyone EC on the final grade!

- So, get em done!

<br>

**Refresh my memory, why do scientists need research questions?**

- (**SLIDE**)

:::



## Why do we need a research question? {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

A research question **focuses** your work, **drives** your progress and let's you know when you're **done**

::: notes

**Refresh my memory, what makes a question a "research" question?**

- (**SLIDE**: Per Huntington-Klein there are two requirements)

:::



## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Research Questions (Huntington-Klein 2022)**

1. Can be answered

2. Improves our understanding of the world

:::

::: notes

**Does this resonate differently now that we've done this exercise in class once already? (last week)**

<br>

**And what are the criteria of a good research question we discussed?**

- (**SLIDE**)

:::



## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Research Questions (Huntington-Klein 2022)**
:::

<br>

**How Do You Know if You’ve Got a Good One?**

- Consider Potential Results

- Consider Feasibility

- Consider Scale

- Consider Design

- Keep It Simple!


::: notes

Per Huntington-Klein, we should focus our research efforts on questions we are likely able to answer with the resources available to us.

<br>

That means we should: 

- **Consider Potential Results**: "If you can’t say something interesting about your potential results, that probably means your research question and your theory aren’t as closely linked as you think!"

- **Consider Feasibility**: "A research question should be a question that can be answered using the right data, if the right data is available. But is the right data available?"

- **Consider Scale**: "What kind of resources and time can you dedicate to answering the research question? ... Given the confines of, say, a term paper, you could take some wild swings at that question, but you’re likely to do a much more thorough job answering questions with a lot less complexity."

- **Consider Design**: "So, an important part of evaluating whether you have a workable research question is figuring out if there’s a reasonable research design you can use to answer it. Figuring out whether you do have a reasonable research design is the topic of the rest of this book."

- **Keep It Simple!**: "Answering any research question can be difficult. Don’t make it even harder on yourself by biting off more than you can chew!"

<br>

So, a research question:

1. Can be answered,

2. Improves our understanding of the world, and 

3. Is feasible given our reseources

<br>

**Questions on any of this?**

<br>

**SLIDE**: To your work!

:::




## For Today {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### Research Questions to Explore the Intersection of the Internet and Terrorism

::: notes

For today I asked each of you to submit and explain a research question we could use to push forward our knowledge of terrorism in the world today.

- **Everybody ready to go with this?**

<br>

*Split class into four groups, work with new people!*

- *I'd prefer smaller groups BUT there's only so much board space*

- Go sit with your new group!

<br>

**SLIDE**: Groups choose/refine a research question

:::



## Developing a Research Proposal {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### 1. Select a research question for your group

- Write the question on the board

- Draw a simple DAG below the question

```{r, fig.retina = 3, fig.align = 'center', fig.width = 6, fig.height=.85, out.width='85%'}
## Manual DAG
d1 <- tibble(
  x = c(-3, 3),
  y = c(1, 1),
  labels = c("Predictor", "Outcome")
)

ggplot(data = d1, aes(x = x, y = y)) +
  geom_point(size = 8) +
  theme_void() +
  coord_cartesian(xlim = c(-4, 4)) +
  geom_label(aes(label = labels), size = 7) +
  annotate("segment", x = -1.9, xend = 1.9, y = 1, yend = 1, arrow = arrow())
```

::: notes

Groups, pick the RQ you want to work on in class today

- Can be one of the ones submitted to Canvas or something new

<br>

Once you have your RQ:

1. Write it on the board, and

2. Summarize the question with a directed acyclic graph (DAG)

<br>

**Questions?**

- Go!

<br>

*PRESENT and DISCUSS each*

- Groups, take a moment to address the feedback you get from this

<br>

**SLIDE**: Theory

:::



## Developing a Research Proposal {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### 2. Propose a theory

- List the reasons your predictor causes your outcome

::: notes

Groups, your next job is to propose a theory that answers this question

- In other words, you need to explain the arrow in the DAG

<br>

Think of this like diagramming an argument

- You are arguing that these two concepts are linked by a causal mechanism (e.g. changes in the predictor lead to changes in the outcome)

- Give us the reasons on the board WHY you think this is true

<br>

**Questions?**

- Go!

<br>

*PRESENT and DISCUSS each*

- Groups, take a moment to address the feedback you get from this

<br>

**SLIDE**: Data needs

:::



## Developing a Research Proposal {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### 3. Describe your data needs

- What is the ideal type of data you would need?

- Do a web search and see if it exists

::: notes

Groups, you now have a question and a theory that suggests an answer to it

- The next step is to identify the kinds of specific measures you would need to answer this question and test your theory

<br>

1. Make sure you understand what kind of measures you would need to answer your question, then

2. Do a simple web search and look to see if this data exists!

<br>

**Questions?**

- Go!

<br>

*PRESENT and DISCUSS each*

<br>

**SLIDE**: Wrap it up

:::



## For Today {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### Research Questions to Explore the Intersection of the Internet and Terrorism

::: notes

**Ok, where do we end up with this?**

- **Groups, do you feel like you have the makings of a real research project here? One that is doable AND would improve our understanding of the world?**

<br>

**Any lessons for the next time you do an exercise like this?**

- **Anything you've learned from this you would apply next time?**

<br>

**SLIDE**: Next class

:::



## For Next Class {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### TBD

::: notes

Details on Canvas

- **Questions on the assignment?**

<br>

Canvas Assignment: ...

:::





