---
format: revealjs
---

## Today's Agenda {background-image="Images/00-Leviathan_Cover_55.png" .center}

```{r}
library(tidyverse)
library(readxl)
library(kableExtra)
```

<br>

**III. How and why do non-state actors use political violence?**

<br>

- Brainstorming a political violence research project

<br>

::: r-stack
Justin Leinaweaver (Fall 2025)
:::

::: notes
Prep for Class

1. Review submissions on Canvas

2. Markers x 4

<br>

**SLIDE**: IDEA evals

:::




## Course Evaluations (IDEA) {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

::: {.r-fit-text}
[https://drury.campuslabs.com/eval-home/](https://drury.campuslabs.com/eval-home/)
:::

::: notes

The link for the IDEA evaluations is here.

- I'll give you ten minutes to complete them

- Super important feedback and I appreciate you taking the time to do it

<br>

IFF everyone in class submits their evals for this class I will give everyone EC on the final grade!

- So, get em done!

<br>

**Refresh my memory, why do scientists need research questions?**

- (**SLIDE**)

:::



## Why do we need a research question? {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

A research question **focuses** your work, **drives** your progress and let's you know when you're **done**

::: notes

**Refresh my memory, what makes a question a "research" question?**

- (**SLIDE**: Per Huntington-Klein there are two requirements)

:::



## {background-image="Images/00-Leviathan_Cover_55.png" .center}

::: {.r-fit-text}
**Research Questions (Huntington-Klein 2022)**

1. Can be answered

2. Improves our understanding of the world

:::

<br>

"A good test for whether a research question informs theory is to imagine that you find an unexpected result, and then wonder whether it would make you change your understanding of the world."

::: notes

**Does this resonate differently now that we've done this exercise in class once already? (last week)**

<br>

**SLIDE**: To your work!

:::




## For Today {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### Research Questions to Explore the Intersection of the Internet and Terrorism

::: notes

For today I asked each of you to submit and explain a research question we could use to push forward our knowledge of terrorism in the world today.

- **Everybody ready to go with this?**

<br>

*Split class into four groups, work with new people!*

- *I'd prefer smaller groups BUT there's only so much board space*

- Go sit with your new group!

<br>

**SLIDE**: Groups choose/refine a research question

:::



## Developing a Research Proposal {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### 1. Select a research question for your group

- Write the question on the board

- Draw a simple DAG below the question

```{r, fig.retina = 3, fig.align = 'center', fig.width = 6, fig.height=.85, out.width='85%'}
## Manual DAG
d1 <- tibble(
  x = c(-3, 3),
  y = c(1, 1),
  labels = c("Predictor", "Outcome")
)

ggplot(data = d1, aes(x = x, y = y)) +
  geom_point(size = 0) +
  theme_void() +
  coord_cartesian(xlim = c(-4, 4)) +
  geom_label(aes(label = labels), size = 7) +
  annotate("segment", x = -1.9, xend = 1.9, y = 1, yend = 1, arrow = arrow())
```

::: notes

Groups, pick the RQ you want to work on in class today

- Can be one of the ones submitted to Canvas or something new

<br>

Once you have your RQ:

1. Write it on the board, and

2. Summarize the question with a directed acyclic graph (DAG)

<br>

**Questions?**

- Go!

<br>

*PRESENT and DISCUSS each*

- Groups, take a moment to address the feedback you get from this

<br>

**SLIDE**: Theory

:::



## Developing a Research Proposal {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### 2. Propose a theory

- List the reasons your predictor causes your outcome

::: notes

Groups, your next job is to propose a theory that answers this question

- In other words, you need to explain the arrow in the DAG

<br>

Think of this like diagramming an argument

- You are arguing that these two concepts are linked by a causal mechanism (e.g. changes in the predictor lead to changes in the outcome)

- Give us the reasons on the board WHY you think this is true

<br>

**Questions?**

- Go!

<br>

*PRESENT and DISCUSS each*

- Groups, take a moment to address the feedback you get from this

<br>

**SLIDE**: Data needs

:::



## Developing a Research Proposal {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### 3. Describe your data needs

- What is the ideal type of data you would need?

- Do a web search and see if it exists

::: notes

Groups, you now have a question and a theory that suggests an answer to it

- The next step is to identify the kinds of specific measures you would need to answer this question and test your theory

<br>

1. Make sure you understand what kind of measures you would need to answer your question, then

2. Do a simple web search and look to see if this data exists!

<br>

**Questions?**

- Go!

<br>

*PRESENT and DISCUSS each*

<br>

**SLIDE**: Wrap it up

:::



## For Today {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

### Research Questions to Explore the Intersection of the Internet and Terrorism

::: notes

**Ok, where do we end up with this?**

- **Groups, do you feel like you have the makings of a real research project here? One that is doable AND would improve our understanding of the world?**

<br>

**Any lessons for the next time you do an exercise like this?**

- **Anything you've learned from this you would apply next time?**

<br>

**SLIDE**: Next class

:::



## For Next Class {background-image="Images/00-Leviathan_Cover_55.png" .center}

<br>

**What is ONE institutional design that currently exists in the US that makes us vulnerable to political violence?**

- See details on Canvas


::: notes

To set us up for the final paper I want us to collect arguments and data focused on what you see as the vulnerabilities in our system.

- What is ONE institutional design that currently exists in the US that makes us vulnerable to political violence? 

- In other words, what is an aspect of our community that creates or allows for acts of political violence to occur? 

- This can be a formal institution (e.g. laws, policies, regulations, constitutional provisions, etc) or an informal one (e.g. norms, customs, etc).

<br>

Two important notes:

1. NO overlap with the other submitted cases (e.g. an institution x a specific vulnerability). 

    - Multiple people can submit the same institution or the same vulnerability, but only one can claim a specific pairing.
    
2. I'm not asking you to "fix" it or to make the argument that the institution must change

    - I simply want us to identify the interactions between institutional design and risk.

<br>

**Questions on the assignment?**

<br>

Canvas Assignment: Identifying Vulnerabilities

What is ONE institutional design that currently exists in the US that makes us vulnerable to political violence? In other words, what is an aspect of our community that creates or allows for acts of political violence to occur? This can be a formal institution (e.g. laws, policies, regulations, constitutional provisions, etc) or an informal one (e.g. norms, customs, etc).

Please try to avoid exact overlap with the other submitted cases (e.g. an institution x a specific vulnerability). Multiple people can submit the same institution or the same vulnerability, but only one can claim a specific pairing.

Please note, I am not asking you to make the argument that your selected institution must change. I simply want us to identify the interactions between institutional design and risk.

1. What is the specific institution you are focused on? (explain your selection and cite evidence it exists)
2. How does that specific institution create a vulnerability to political violence? (explain the causal mechanism as clearly as you can, 3-5 sentences)
3. Submit a piece of evidence that illustrates this dynamic in action (APA citation and explanation of the evidence)

:::





